Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-01-22 paper.tex
Make several miscellaneous fixes.

Earlier work by Mosher et al.~\cite{Mosher1993Error} also sought to derive
lower bounds on source localization accuracy by deriving Cramer-Rao lower
bounds. They also have some preliminary numerical results showing improvement
with increased numbers of sensors. However, this result is also not completely
satisfactory because Cramer-Rao bounds do not apply to biased estimators.
Commonly used source localization algorithms (such as the Minimum Norm
Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are \emph{known}
to be biased~\cite{Lin2006Assessing}.

@@

The one-dimensional toy problem is an effective tool for understanding bounds
on source localization accuracy in other settings as well, such as
\textcolor{red}{<insert other applications>}. A vast literature on linear
inverse problems (see~\cite{Bal2012Introduction} for an introduction to this
field) and deconvolution algorithms exists, and has addressed the reduced
one-dimensional problem in broad settings
(see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
references therein). However, our setting and interpretation appears to be
unique, since most prior work focuses on recovering a whole function (given
certain smoothness constraints), rather than locating a point source. Work that
does address point sources, to our knowledge, does not address scaling in the
number of sensors, since problem settings and applications differ greatly.

@@

We assume that the point source is located on a circle of circumference $S$ (a
circular domain enables us to use symmetry arguments to simplify the proof). We
can view this domain as a line, on which signals are periodic with period $S$.
The point source is therefore located somewhere within one period. We denote
the set of possible locations by $\Theta = [0, S)$. Due to the periodic nature
of the domain, a source located at position $\theta \in \Theta$ implies the
presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$.

@@

Sensors are assumed to be uniformly distributed over the domain, i.e., if there
are $m$ sensors, they are placed at locations $s = 0$, $S/m$, $2S/m$,~\dots,
$(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
generality we take it to be 0). The periodicity of the space ensures that we
automatically also have sensors at $S$, $S{+}S/m$,~\dots\@ The lower bounds we
provide, therefore, are for \emph{this specific sensor configuration}. For a
discussion on why this configuration might be an appropriate choice in the
minimax setting, and on non-uniform sensor placement, see
section~\ref{sec:discussion}.

@@

The noise $\v \epsilon$, introduced in equation~\eqref{eq:sensor-obs}, is
the only source of uncertainty in the problem. For our purposes, we assume that
$\v \epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim \mathcal{N}(\v 0, \m
\Sigma)$. Two kinds of covariance matrices are of particular interest. The
first is dubbed the ``sensor noise'' setting, wherein $\m\Sigma = \sigma^2 \m
I$, i.e. the sensors are afflicted by i.i.d.\ noise. The second is called the
``source noise'' setting, wherein $\m\Sigma$ has off-diagonal terms.
\textcolor{red}{Insert description of source noise.}

@@

Consider the following estimation problem: we have $n$ i.i.d.\ random samples
$Y^n$ from a distribution $P$, which is indexed by a parameter $\theta \in
\Theta$.  Denote the set of these distributions by $\mathcal{P} = \{P(\theta) :
\theta \in \Theta\}$. Suppose we now wish to estimate $\theta$ from $Y^n$.
Define a loss metric $\rho(\theta, \hat\theta)$ (e.g.\ $\rho(\theta,
\hat\theta) = \abs{\theta - \hat\theta}$). For this metric, we can define the
minimax risk over all possible estimators $\hat\theta(Y^n)$ and all possible
$\theta \in \Theta$:
\begin{equation} \label{eq:minimax-expr}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \inf_{\hat\theta} \sup_{\theta \in \Theta} \mathbb E[\Phiorho (\hat\theta(Y^n), \theta)]
\end{equation}
where $\Phi$ is any non-decreasing function (e.g.\ $\Phi(\rho) = \rho^2$) and
$Y^n$ is the random vector corresponding to a noisy realization of sensor
values.

We start by lower bounding the minimax risk of the estimation problem with the
risk incurred in a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing:%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if
	\begin{equation}
		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
	\end{equation}
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown, true hypothesis, and $\psi$ is our estimate of
	the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader to Proposition~13.3
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:est-to-testing}
says that the error in estimating $\theta_i$ is likely to be more if it is
difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
of error is high (where $\theta_j$ has been selected to be suitably close).

We now need to lower bound the probability of error in the hypothesis testing
problem. The simplest way to do this is to consider a binary hypothesis test
($\abs{\mathcal{V}} = 2$) and use what is known as Le Cam's method:
\begin{theorem} \label{thm:le-cam}
	For a binary hypothesis test, i.e., when $\mathcal{V} = \{0, 1\}$,
	\begin{equation}
		\inf_\psi \mathbb P(\psi(Y^n) \neq V) = 1 - \norm{P_0 - P_1}_{TV}
	\end{equation}
	where $P_i$ is short-hand for $P(\theta_i)$ and $\norm{P_0 - P_1}_{TV}$ is
	the total variation distance between the two distributions, defined as
	$\norm{\cdot}_{TV} = \frac{1}{2} \norm{\cdot}_1$.
\end{theorem}
For a proof, we refer the reader to Proposition~2.11
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:le-cam} states
that the minimum probability of error that any estimator must make in a binary
hypothesis testing problem is related to the distance between the distributions
corresponding to the two hypotheses. The closer the two distributions, the
higher the chance of making an error in distinguishing between them.

@@

We now state the main result of this paper.
\begin{theorem} \label{thm:main-lb}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
	location of a point source is lower bounded by:
	\begin{equation} \label{eq:main-lower-bound}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}
	\end{equation}
\end{theorem}

\begin{IEEEproof}
Starting from equation~\eqref{eq:le-cam-bound} and working on the setting
described in Section~\ref{sec:source-localization}, we proceed to derive the
total variation distance for the distributions of interest. Using Pinsker's
inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
KL-divergence~\cite{Duchi2015Information}, we see that:
\begin{equation} \label{eq:pinsker-tensorization}
	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
\end{equation}
For multivariate normal distributions with the same covariance, the
KL-divergence is given by
\begin{equation} \label{eq:kl-div-normal}
	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
\end{equation}
where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
respectively~\cite{DuchiDerivation}.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{S}}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kS}{m}; \theta_0\Big) - x\Big(\frac{kS}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(s;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
equal to the number of sensors in the total region covered by the signals
$x(s;\theta_0)$ and $x(s;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{S} + 1}$, since at most a fraction $(w + 2\delta) / S$ of the $m$
sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
hence
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{S} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{S} + 1\Big).
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $s=0$, for
example). \textcolor{blue}{In such a case, one part of the signal $x(s;\theta_0)$ will appear at
the left edge of the domain, and the remaining part will appear as the
repetition from the period $[S, 2S)$, at the right edge of the domain.} Also
note that the two signals $x(s;\theta_0)$ and $x(s;\theta_1)$ overlap at most
once, since $w < S/2$, as stated in section~\ref{sec:signal-model}.

@@

\subsection{Towards a more \textcolor{blue}{physical} sensor model}

@@

The looseness lies in a poor sensor model: we assume that an arbitrarily large
number of sensors can be squeezed into a finite amount of space, and that these
sensors \emph{still} give us i.i.d.\ observations, with the same noise
variance. This is an impractical expectation. In reality, sensors have a
certain width, and the signal measured by them is the integral of the
continuous-space signal within that width (this is similar to a sample-and-hold
circuit, which integrates a continuous-\emph{time} signal over a short period).
If the width of a sensor is decreased, then effectively, its signal-to-noise
ratio reduces (this is intuitively evident in the sample-and-hold analogy: to
compute the signal value, the integral must be divided by the time interval
over which the integration is performed; this division amplifies noise as the
time interval gets smaller).

We performed a preliminary study to understand the effect of viewing sensors
as integrators. In the new sensor model, sensors have a finite width, which
decreases as the number of sensors increases, in order to allow their number to
grow unbounded. Concretely, the $k$-th sensor which is located at $s = kS/m$
extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$. The signal
sensed by this sensor is the $k$-th element of $\v x(\theta)$, given by
\begin{equation}
	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds
\end{equation}
\textcolor{red}{Also need to talk about noise here - sensor obs. are still iid
because we assume wss noise, and integrating over distinct regions of this
process retains iid nature}
The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
admits a solution which gives a bound for all values of $m$. We can compute the
bound numerically, however, using exact expressions for error probability in a
binary hypothesis test. For gaussian distributions of equal variance, the best
possible error probability (over all tests) is a Q-function in the distance
between their means:
\begin{equation}
	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma}\bigg)
\end{equation}
\textcolor{red}{Is this definitely correct? i.e.\ the best test is a linear
separator? I think this is coming from Neyman-Pearson. Should I cite?}
The minimax estimation risk is lower bounded by the risk in hypothesis testing,
hence
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma}\bigg).
\end{equation}
This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
separated by a distance of $2\delta$. As the $\delta$ increases, it becomes
easier to distinguish between the two hypotheses, so $P_e$ falls. When
numerically evaluating the bound, therefore, we have to \emph{manually}
trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
hypotheses to distinguish between. To make the simulation easier, we can relax
the process of finding the least discernable hypothesis pair by fixing
$\theta_0$. Then, we need only optimize over $\delta$, making the process more
tractable. This comes at the cost of loosening the lower bound.

>>>>

Earlier work by Mosher et al.~\cite{Mosher1993Error} also sought to derive
lower bounds on source localization error by deriving Cramer-Rao lower bounds.
They also give some preliminary numerical results showing improvement with
increased numbers of sensors. However, this result is also not completely
satisfactory because Cramer-Rao bounds do not apply to biased estimators.
Commonly used source localization algorithms (such as the Minimum Norm
Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are \emph{known}
to be biased~\cite{Lin2006Assessing}.

@@

The one-dimensional toy problem is an effective tool for understanding bounds
on source localization accuracy in other settings as well, such as auditory
localization of a sound using a microphone array (although typically, very
different approaches are employed there, when compared to EEG source
localization). A vast literature on linear inverse problems
(see~\cite{Bal2012Introduction} for an introduction to this field) and
deconvolution algorithms exists, and has addressed the reduced one-dimensional
problem in broad settings
(see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
references therein). However, our setting and interpretation appears to be
unique, since most prior work focuses on recovering a whole function (given
certain smoothness constraints), rather than locating a point source. Work that
does address point sources, to our knowledge, does not address scaling in the
number of sensors, since problem settings and applications differ greatly.

@@

We assume that the point source is located on a circle of circumference $S$ (a
circular domain enables us to use symmetry arguments to simplify the proof). We
can view this domain as a line, on which signals are periodic with period $S$.
The point source is therefore located somewhere within one period. We denote
the set of possible locations by $\Theta = [0, S)$. Due to the periodic nature
of the domain, a source located at position $\theta \in \Theta$ implies the
presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$ (using
`$s$' for the spatial variable).

@@

Sensors are assumed to be uniformly distributed over the domain, i.e., if there
are $m$ sensors, they are placed at locations $s = 0$, $S/m$, $2S/m$,~\dots,
$(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
generality we take it to be 0). The periodicity of the space ensures that we
automatically also have sensors at $S$, $S{+}S/m$,~\dots\@ The lower bounds we
provide are for \emph{this specific sensor configuration}. For a discussion on
why this configuration might be an appropriate choice in the minimax setting,
and on non-uniform sensor placement, see section~\ref{sec:discussion}.

@@

The noise $\v \epsilon$, introduced in equation~\eqref{eq:sensor-obs}, is
the only source of uncertainty in the problem. For our purposes, we assume that
$\v \epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim \mathcal{N}(\v 0, \m
\Sigma)$. Two kinds of covariance matrices are of particular interest. The
first is dubbed the ``sensor noise'' setting, wherein $\m\Sigma = \sigma^2 \m
I$, i.e. the sensors are afflicted by i.i.d.\ noise. The second is called the
``source noise'' setting, wherein $\m\Sigma$ has off-diagonal terms. \textcolor{blue}{We
restrict our attention to the sensor noise setting in this paper.}

@@

Consider the following estimation problem: we have $n$ i.i.d.\ random samples
$Y^n$ from a distribution $P$, which is indexed by a parameter $\theta \in
\Theta$.  Denote the set of these distributions by $\mathcal{P} = \{P(\theta) :
\theta \in \Theta\}$. Suppose we now wish to estimate $\theta$ from $Y^n$.
Define a loss metric $\rho(\theta, \hat\theta)$ (e.g.\ $\rho(\theta,
\hat\theta) = \abs{\theta - \hat\theta}$). For this metric, we can define the
minimax risk over all possible estimators $\hat\theta(Y^n)$ and all parameters
$\theta \in \Theta$:
\begin{equation} \label{eq:minimax-expr}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \inf_{\hat\theta} \sup_{\theta \in \Theta} \mathbb E[\Phiorho (\hat\theta(Y^n), \theta)]
\end{equation}
where $\Phi$ is any non-decreasing function (e.g.\ $\Phi(\rho) = \rho^2$).

We start by lower bounding the minimax risk of the estimation problem with the
risk incurred in a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing:%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if
	\begin{equation}
		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
	\end{equation}
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown true hypothesis which takes values uniformly from
	$\mathcal{V}$, and $\psi$ is our estimate of the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader to Proposition~13.3
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:est-to-testing}
says that the error in estimating $\theta_i$ is likely to be more if it is
difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
of error is high.

We now need to lower bound the probability of error in the hypothesis testing
problem. The simplest way to do this is to consider a binary hypothesis test
and use what is known as Le Cam's method:
\begin{theorem} \label{thm:le-cam}
	For a binary hypothesis test, i.e., $\mathcal{V} = \{0, 1\}$,
	\begin{equation}
		\inf_\psi \mathbb P(\psi(Y^n) \neq V) = 1 - \norm{P_0 - P_1}_{TV}
	\end{equation}
	where $P_i$ is short-hand for $P(\theta_i)$ and $\norm{P_0 - P_1}_{TV}$ is
	the total variation distance between the two distributions, defined as
	$\norm{\cdot}_{TV} = \frac{1}{2} \norm{\cdot}_1$.
\end{theorem}
For a proof, we refer the reader to Proposition~2.11
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:le-cam} states
that the minimum achievable error probability in a binary hypothesis testing
problem is related to the distance between the distributions corresponding to
the two hypotheses.

@@

We now state the main result of this paper.
\begin{theorem} \label{thm:main-lb}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
	location of a point source is lower bounded by
	\begin{equation} \label{eq:main-lower-bound}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}.
	\end{equation}
\end{theorem}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{S} + 1}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

\begin{IEEEproof}
Starting from equation~\eqref{eq:le-cam-bound}, we proceed to derive the total
variation distance for the distributions of interest. Using Pinsker's
inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
KL-divergence~\cite{Duchi2015Information}, we see that:
\begin{equation} \label{eq:pinsker-tensorization}
	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
\end{equation}
For multivariate normal distributions with the same covariance, the
KL-divergence is given by
\begin{equation} \label{eq:kl-div-normal}
	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
\end{equation}
where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
respectively~\cite{DuchiDerivation}. For the case of sensor noise, $P_i =
\mathcal{N}(\v x(\theta_i), \sigma^2 \m I)$, as described in
section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and $0$ otherwise). Then, we have
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kS}{m}; \theta_0\Big) - x\Big(\frac{kS}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k)
\end{align}
where $x(s;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
equal to the number of sensors in the total region covered by the signals
$x(s;\theta_0)$ and $x(s;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{S} + 1}$, since at most a fraction $(w + 2\delta) / S$ of the $m$
sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
hence
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{S} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{S} + 1\Big).
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $s=0$, for
example). \textcolor{blue}{In such a case, one part of the signal $x(s;\theta_0)$ will appear at
the left edge of the domain, and the remaining part will appear as the
repetition from the period $[S, 2S)$, at the right edge of the domain.} Also
note that the two signals $x(s;\theta_0)$ and $x(s;\theta_1)$ overlap at most
once, since $w < S/2$, as stated in section~\ref{sec:signal-model}.

@@

\subsection{Towards a more physical sensor model}

@@

The looseness lies in a poor sensor model: we assume that an arbitrarily large
number of sensors can be squeezed into a finite amount of space, and that these
sensors \emph{still} give us i.i.d.\ observations, with the same noise
variance. This is an impractical expectation. In reality, sensors have a
certain width, and the signal measured by them is the integral of the
continuous-space signal within that width (analogous to a sample-and-hold
circuit, which integrates a continuous-\emph{time} signal over a short period).
If the width of a sensor is decreased, then effectively, its signal-to-noise
ratio reduces (this is intuitively evident in the sample-and-hold analogy: to
compute the signal value, the integral must be divided by the time interval
over which the integration is performed; this division amplifies noise as the
time interval gets smaller).

We performed a preliminary study to understand the effect of viewing sensors
as integrators. In the new sensor model, sensors have a finite width, which
decreases as the number of sensors increases, in order to allow their number to
grow unbounded. Concretely, the $k$-th sensor which is located at $s = kS/m$
extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$. The signal
sensed by this sensor is the $k$-th element of $\v x(\theta)$, now given by
\begin{equation}
	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds
\end{equation}
The noise vector $\v \epsilon$ is also generated similarly, by integrating over
small sections of a wide-sense-stationary white noise process, which is assumed
to additively corrupt the signal. This leads to i.i.d.\ noise values at sensors
(since they do not overlap), with variance inversely proportional to $m$, i.e.,
$\sigma(m) \propto 1/\sqrt{m}$.

The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
admits a solution which gives a bound for all values of $m$. We can compute the
bound numerically, however, using exact expressions for error probability in a
binary hypothesis test. For gaussian distributions of equal variance, the best
possible error probability (over all tests) is a Q-function in the distance
between their means:
\begin{equation}
	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma(m)}\bigg)
\end{equation}
\textcolor{red}{Is this definitely correct? i.e.\ the best test is a linear
separator? I think this is coming from Neyman-Pearson. Should I cite?}
The minimax estimation risk is lower bounded by the risk in hypothesis testing,
hence
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma(m)}\bigg).
\end{equation}
This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
separated by a distance of $2\delta$. As the $\delta$ increases, it becomes
easier to distinguish between the two hypotheses, so $P_e$ falls. When
numerically evaluating the bound, therefore, we have to \emph{manually}
trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
hypotheses to distinguish between. To make the simulation easier, we can relax
the process of finding the least discernable hypothesis pair by fixing
$\theta_0$. Then, we need only optimize over $\delta$, making the process more
tractable. This comes at the cost of loosening the lower bound.
